Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-08-15 paper/paper.tex
A pretty graph
More experiments to do

\include{preamble}

@@

\section{Domain Filtering}

@@

\section{Filtering During Search}

@@

@@

@@

>>>>

\usepackage[pass]{geometry}

\usepackage{ijcai16}
\usepackage{times}
\usepackage{complexity}
\usepackage{microtype}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{cleveref}
\usepackage{tikz}
\usepackage{mathtools}
\usepackage{graphicx}

\usepackage{showframe}

\makeatletter\@ifpackageloaded{showframe}{
    % show lines down the middle columns too
    % http://tex.stackexchange.com/questions/16199/test-if-a-package-or-package-option-is-loaded
\newlength\Fcolumnseprule\setlength\Fcolumnseprule{0.4pt}\def\@outputdblcol{%
  \if@firstcolumn\global \@firstcolumnfalse \global \setbox\@leftcolumn \box\@outputbox
  \else
    \global \@firstcolumntrue
    \setbox\@outputbox \vbox{\hb@xt@\textwidth{\hb@xt@\columnwidth{\box\@leftcolumn \hss}%
    \vrule \@width\Fcolumnseprule\hfil{\normalcolor\vrule \@width\columnseprule}
    \hfil\vrule \@width\Fcolumnseprule\hb@xt@\columnwidth {\box\@outputbox \hss}}}\@combinedblfloats\@outputpage
    \begingroup\@dblfloatplacement\@startdblcolumn\@whilesw\if@fcolmade \fi{\@outputpage\@startdblcolumn}\endgroup
  \fi
}}{}
\makeatother

\usetikzlibrary{decorations, decorations.pathreplacing, calc, backgrounds}

\definecolor{uofgsandstone}{rgb}{0.321569, 0.278431, 0.231373}
\definecolor{uofglawn}{rgb}{0.517647, 0.741176, 0}
\definecolor{uofgcobalt}{rgb}{0, 0.615686, 0.92549}
\definecolor{uofgpumpkin}{rgb}{1.0, 0.72549, 0.282353}
\definecolor{uofgthistle}{rgb}{0.584314, 0.070588, 0.447059}

\newcommand{\citet}[1]{\citeauthor{#1} \shortcite{#1}}
\newcommand{\citep}[1]{\cite{#1}}

\theoremstyle{definition}
\newtheorem{proposition}{Proposition}

% cref style
\crefname{figure}{Figure}{Figures}
\Crefname{figure}{Figure}{Figures}

% http://tex.stackexchange.com/questions/22100/the-bar-and-overline-commands
\newcommand{\shortoverline}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}

% Maths operators
\newcommand{\nds}{\operatorname{nds}}
\newcommand{\lessnonind}[1]{\prescript{}{#1}{\rightarrowtail}\ }
\newcommand{\lessind}[1]{\prescript{}{#1}{\hookrightarrow}\ }

% to do comments
\usepackage{color}
\newcommand{\todo}[1]{{\color{red} {[}{#1}{]}}}

@@

\section{Domain Filtering using Degrees}

@@

In \cref{figure:ids} we show that this is useful in practice.

\begin{figure}
    \includegraphics*{gen-graph-ids.pdf}
    \caption{We get domain filtering. Woohoo.}\label{figure:ids}
\end{figure}

\section{Filtering During Search Using Paths}

@@

To allow for fast propagation, we create supplemental graphs for paths of length 2, looking at
counts of 1, 2, and 3 in the target graph (and so counts of $1 + k$ up to $3 + k$ in the pattern).
We then investigate whether this leads to new constraints being generated. By an assignment, we mean
considering mapping a pattern vertex $p$ to a target vertex $t$ (and not $\bot$) which does not
violate any loop constraints. An assignment pair is two assignments with distinct $p$ and distinct
$t$, which we say is permitted if it does not violate any adjacency constraint. We define the
permitted assignment pair ratio to be the proportion of assignment pairs which are permitted.
Finally, we scatter plot the permitted assignment pair ratio with and without supplemental
graphs\footnote{Because of the large sizes of the domains, we randomly sample one million pairs
rather than considering every pair. In some cases, we have nearly a thousand domains, each with nearly
ten thousand values---a complete quadratic calculation involving even a trivial arithmetic operation
on this would take many hours.}. For $k = 0$, we see many points above the $x-y$ diagonal, which
shows that for many instances, we are able to create a substantial number of new constraints at the
top of search; on the other hand, there are also points on the diagonal, which shows that sometimes
this technique provides no benefit. (Occasionally, points fall below the $x-y$ diagonal. This is
because the use of neighbourhood degree sequence reasoning on supplemental graphs can also lead to
increased domain filtering, which could in turn eliminate a higher proportion of forbidden than
permitted assignment pairs.) For $k = 1$ and $k = 2$, the proportion of points above the diagonal
diminishes, but we are still able to create new constraints for many instances. By the time $k = 3$,
most of the benefit is disappearing---although sometimes we are still able to make a difference, and
bear in mind that sometimes adding just one new constrained pair can vastly reduce the search space.

A closer inspection of the raw data shows that for $k = 3$, nearly all of the instances showing a
strong improvement are from the ``LV'' family of graphs.

\begin{figure*}
    \includegraphics*{gen-graph-constraints.pdf}\\[0.1cm]
    \includegraphics*{gen-graph-constraints-induced.pdf}
    \caption{We get new constraints. More woohoo.}\label{figure:constraints}
\end{figure*}

@@

\begin{figure}
    \includegraphics*{gen-graph-runtimes.pdf}
    \caption{Look how amazing our stuff is.}\label{figure:runtimes}
\end{figure}

@@

What proportion of instances are actually satisfiable as $k$ increases?
